quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-12 paper-quollr.Rmd
Updated the MSE plot

```{r model-limb, fig.cap="Compare the published $2-\\text{D}$ layout (\\@ref(fig:nldr-layouts) b) and the $2-\\text{D}$ layout selected (\\@ref(fig:nldr-layouts) f) by RMSE plot (\\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$.", out.width="100%", fig.width=10, fig.height=15}

trimesh_limb + trimesh_limb_best +
  trimesh_limb + trimesh_limb_best +
  trimesh_limb + trimesh_limb_best +
  plot_layout(ncol = 2)
```

>>>>

```{r model-limb, fig.cap="Compare the published $2-\\text{D}$ layout (\\@ref(fig:nldr-layouts) b) and the $2-\\text{D}$ layout selected (\\@ref(fig:nldr-layouts) f) by RMSE plot (\\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$.", out.width="100%", fig.width=15, fig.height=10}

trimesh_limb + trimesh_limb_best +
  trimesh_limb + trimesh_limb_best +
  trimesh_limb + trimesh_limb_best +
  plot_layout(nrow = 2)
```
